19Q2

### 2020-01-06 19Q2.Rmd

crispr_cn_ht2 <- MakeCorrHeatmap(cor_res = crispr_cn_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "CRISPR", color_range = c(-0.25, 0, 0.25), radius = 0.15, legend_title = "Copy num. Spearman correlation", metric = "CN")
ccle_cn_ht2 <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num. Spearman correlation", metric = "CN")
ctrp_cn_ht2 <- MakeCorrHeatmap(cor_res = ctrp_cn_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num. Spearman correlation", metric = "CN")
gdsc_cn_ht2 <- MakeCorrHeatmap(cor_res = gdsc_cn_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num. Spearman correlation", metric = "CN")
png(filename = "./plots/manuscript/all_cn_heatmap.png", width = 13, height = 3.5, units = "in", res = 500)
draw(crispr_cn_ht2 +ccle_cn_ht2 + ctrp_cn_ht2 + gdsc_cn_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()

@@

```{r fig.height=8, fig.width=15, eval=FALSE}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.15)
ht_mut_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
ht_mut_grob <- grid.grabExpr(draw(ht_mut_list, gap = unit(0.25, "in"), heatmap_legend_side = "top"))

@@

crispr_mut_filt <- filter(crispr, Gene %in% filter(crispr_signif_g2p_dg_summ, p < 0.05)$Gene)
crispr_mut_filt_plot <- ggplot(data = crispr_mut_filt, aes(x = as.character(Mutation), y = Score) )+
  facet_wrap(~ Gene, ncol = 5) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
  labs(title = "CRISPR", x = "Mutation Status") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "snow1", colour = "snow1", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

ccle_mut_filt <- filter(ccle, Drug_Gene %in% filter(ccle_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
ccle_mut_filt_plot <- ggplot(data = ccle_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  facet_wrap(~ Drug_Gene, ncol = 5) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
  labs(title = "CCLE", x = "Mutation Status") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

ctrp_mut_filt <- filter(ctrp, Drug_Gene %in% filter(ctrp_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
ctrp_mut_filt_plot <- ggplot(data = ctrp_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  facet_wrap(~ Drug_Gene, ncol = 7) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07,) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
  labs(title = "CTRP", x = "Mutation Status") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

gdsc_mut_filt <- filter(gdsc, Drug_Gene %in% filter(gdsc_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
gdsc_mut_filt_plot <- ggplot(data = gdsc_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  facet_wrap(~ Drug_Gene, ncol = 5) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07, ) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "turquoise4", "0" = "paleturquoise3")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
  labs(title = "GDSC", x = "Mutation Status") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "lightcyan", colour = "lightcyan", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

@@

png(filename = "./plots/manuscript_final/all_mutation_agnostic_boxplots.png", width = 15, height = 15, units = "in", res = 500)
grid.arrange(layout_matrix = lay,
             arrangeGrob(ht_mut_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(crispr_mut_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(ccle_mut_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(ctrp_mut_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(gdsc_mut_filt_plot), left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
dev.off()
```

@@

```{r prot_changes, eval = FALSE, fig.height=15, fig.width=15}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.009)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.135)
ht_prot_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
ht_prot_grob <- grid.grabExpr(draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "top"))

@@

crispr_prot_filt <- filter(crispr_prot, Gene_Protein_Change %in% filter(crispr_signif_prot_summ, p < 0.05)$Gene_Protein_Change)
crispr_prot_filt_plot <- ggplot(data = crispr_prot_filt, aes(x = as.character(Change_Status), y = Score) )+
  facet_wrap(~ Gene_Protein_Change, nrow = 2) +
  geom_violin(aes(fill = as.character(Change_Status))) +
  geom_boxplot(outlier.shape = NA, width = 0.07) +
  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
  scale_fill_manual(name = "Protein Change Status", labels = c("Wildtype", "Mutant"), values = c("Yes" = "darkorchid", "No" = "thistle")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
  labs(title = "CRISPR", x = "Protein Change Status") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "snow1", colour = "snow1", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

@@

ctrp_prot_filt <- filter(ctrp_prot, Drug_Gene_Protein_Change %in% filter(ctrp_signif_prot_summ, p < 0.05)$Drug_Gene_Protein_Change)
ctrp_prot_filt_plot <- ggplot(data = ctrp_prot_filt, mapping = aes(x = as.character(Change_Status), y = Score)) +
  facet_wrap(~ Drug_Gene_Protein_Change, nrow = 2) +
  geom_violin(aes(fill = as.character(Change_Status))) +
  geom_boxplot(outlier.shape = NA, width = 0.07,) +
  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
  scale_fill_manual(name = "Protein Change Status", labels = c("Wildtype", "Mutant"), values = c("Yes" = "steelblue4", "No" = "slategray3")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
  labs(title = "CTRP", x = "Protein Change Status") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

gdsc_prot_filt <- filter(gdsc_prot, Drug_Gene_Protein_Change %in% filter(gdsc_signif_prot_summ, p < 0.05)$Drug_Gene_Protein_Change)
gdsc_prot_filt_plot <- ggplot(data = gdsc_prot_filt, mapping = aes(x = as.character(Change_Status), y = Score)) +
  facet_wrap(~ Drug_Gene_Protein_Change, nrow = 2) +
  geom_violin(aes(fill = as.character(Change_Status))) +
  geom_boxplot(outlier.shape = NA, width = 0.07, ) +
  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
  scale_fill_manual(name = "Protein Change Status", labels = c("Wildtype", "Mutant"), values = c("Yes" = "turquoise4", "No" = "paleturquoise3")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
  labs(title = "GDSC", x = "Protein Change Status") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "lightcyan", colour = "lightcyan", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

@@

png(filename = "./plots/manuscript_final/all_protein_change_agnostic_boxplots.png", width = 15, height = 15, units = "in", res = 500)
grid.arrange(layout_matrix = lay,
             arrangeGrob(ht_prot_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(crispr_prot_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(ctrp_prot_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(gdsc_prot_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
dev.off()
```

**1/3: Need to do CN and GE and lineage specific analyses**

>>>>

crispr_cn_ht2 <- MakeCorrHeatmap(cor_res = crispr_cn_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "CRISPR", color_range = c(-0.25, 0, 0.25), radius = 0.15, legend_title = "Copy num. Spearman correlation", metric = "CN")
ccle_cn_ht2 <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num. Spearman correlation", metric = "CN")
ctrp_cn_ht2 <- MakeCorrHeatmap(cor_res = ctrp_cn_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num. Spearman correlation", metric = "CN")
gdsc_cn_ht2 <- MakeCorrHeatmap(cor_res = gdsc_cn_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num. Spearman correlation", metric = "CN")
png(filename = "./plots/manuscript/all_cn_heatmap.png", width = 13, height = 3.5, units = "in", res = 500)
draw(crispr_cn_ht2 + ccle_cn_ht2 + ctrp_cn_ht2 + gdsc_cn_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()

@@

```{r fig.height=8, fig.width=15, eval=FALSE}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.15)
ht_mut_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
ht_mut_grob <- grid.grabExpr(draw(ht_mut_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))

@@

crispr_mut_filt <- filter(crispr, Gene %in% filter(crispr_signif_g2p_dg_summ, p < 0.05)$Gene)
crispr_mut_filt_plot <- ggplot(data = crispr_mut_filt, aes(x = as.character(Mutation), y = Score) )+
  facet_wrap(~ Gene, ncol = 5) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_y_continuous(breaks = seq(-3, 1, by = 0.5), labels = c("-3.0", "-2.5", "-2.0", "-1.5", "-1.0", "-0.5", "0.0", "0.5", "1.0")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
  labs(title = "CRISPR", x = "Mutation Status", y = "CERES Score") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "snow1", colour = "snow1", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

ccle_mut_filt <- filter(ccle, Drug_Gene %in% filter(ccle_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
ccle_mut_filt_plot <- ggplot(data = ccle_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  facet_wrap(~ Drug_Gene, ncol = 5) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
  labs(title = "CCLE", x = "Mutation Status", y = "AUC") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

ctrp_mut_filt <- filter(ctrp, Drug_Gene %in% filter(ctrp_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
ctrp_mut_filt_plot <- ggplot(data = ctrp_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  facet_wrap(~ Drug_Gene, ncol = 7) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07,) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
  labs(title = "CTRP", x = "Mutation Status", y = "AUC") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

gdsc_mut_filt <- filter(gdsc, Drug_Gene %in% filter(gdsc_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
gdsc_mut_filt_plot <- ggplot(data = gdsc_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  facet_wrap(~ Drug_Gene, ncol = 5) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07, ) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "turquoise4", "0" = "paleturquoise3")) +
  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
  coord_cartesian(ylim = c(0, 1.10)) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
  labs(title = "GDSC", x = "Mutation Status", y = "AUC") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "lightcyan", colour = "lightcyan", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

@@

gs_mut <- gList(arrangeGrob(ht_mut_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(crispr_mut_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(ccle_mut_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(ctrp_mut_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(gdsc_mut_filt_plot), left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))

png(filename = "./plots/manuscript_final/mutation_pancancer_small.png", width = 15, height = 17, units = "in", res = 100)
grid.arrange(layout_matrix = lay, grobs = gs_mut)
dev.off()

png(filename = "./plots/manuscript_final/mutation_pancancer.png", width = 15, height = 17, units = "in", res = 500)
grid.arrange(layout_matrix = lay, grobs = gs_mut)
dev.off()
```

@@

```{r prot_changes, eval = FALSE, fig.height=15, fig.width=15}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.012)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.135)
ht_prot_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
ht_prot_grob <- grid.grabExpr(draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))

@@

crispr_prot_filt <- filter(crispr_prot, Gene_Protein_Change %in% filter(crispr_signif_prot_summ, p < 0.05)$Gene_Protein_Change)
crispr_prot_filt_plot <- ggplot(data = crispr_prot_filt, aes(x = as.character(Change_Status), y = Score) )+
  facet_wrap(~ Gene_Protein_Change, nrow = 2) +
  geom_violin(aes(fill = as.character(Change_Status))) +
  geom_boxplot(outlier.shape = NA, width = 0.07) +
  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
  scale_y_continuous(breaks = seq(-3, 1, by = 0.5), labels = c("-3.0", "-2.5", "-2.0", "-1.5", "-1.0", "-0.5", "0.0", "0.5", "1.0")) +
  scale_fill_manual(name = "Protein Change Status", labels = c("Wildtype", "Mutant"), values = c("Yes" = "darkorchid", "No" = "thistle")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
  labs(title = "CRISPR", x = "Protein Change Status", y = "CERES Score") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "snow1", colour = "snow1", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

@@

ctrp_prot_filt <- filter(ctrp_prot, Drug_Gene_Protein_Change %in% filter(ctrp_signif_prot_summ, p < 0.05)$Drug_Gene_Protein_Change)
ctrp_prot_filt_plot <- ggplot(data = ctrp_prot_filt, mapping = aes(x = as.character(Change_Status), y = Score)) +
  facet_wrap(~ Drug_Gene_Protein_Change, nrow = 2) +
  geom_violin(aes(fill = as.character(Change_Status))) +
  geom_boxplot(outlier.shape = NA, width = 0.07,) +
  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
  coord_cartesian(ylim = c(0, 1.10)) +
  scale_fill_manual(name = "Protein Change Status", labels = c("Wildtype", "Mutant"), values = c("Yes" = "steelblue4", "No" = "slategray3")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
  labs(title = "CTRP", x = "Protein Change Status", y = "AUC") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

gdsc_prot_filt <- filter(gdsc_prot, Drug_Gene_Protein_Change %in% filter(gdsc_signif_prot_summ, p < 0.05)$Drug_Gene_Protein_Change)
gdsc_prot_filt_plot <- ggplot(data = gdsc_prot_filt, mapping = aes(x = as.character(Change_Status), y = Score)) +
  facet_wrap(~ Drug_Gene_Protein_Change, nrow = 2) +
  geom_violin(aes(fill = as.character(Change_Status))) +
  geom_boxplot(outlier.shape = NA, width = 0.07, ) +
  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
  coord_cartesian(ylim = c(0, 1.10)) +
  scale_fill_manual(name = "Protein Change Status", labels = c("Wildtype", "Mutant"), values = c("Yes" = "turquoise4", "No" = "paleturquoise3")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
  labs(title = "GDSC", x = "Protein Change Status", y = "AUC") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "lightcyan", colour = "lightcyan", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

@@

gs_prot <- gList(arrangeGrob(ht_prot_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(crispr_prot_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(ctrp_prot_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(gdsc_prot_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))

png(filename = "./plots/manuscript_final/protein_change_pancancer_small.png", width = 15, height = 15, units = "in", res = 100)
grid.arrange(layout_matrix = lay, grobs = gs_prot)
dev.off()

png(filename = "./plots/manuscript_final/protein_change_pancancer.png", width = 15, height = 15, units = "in", res = 500)
grid.arrange(layout_matrix = lay, grobs = gs_prot)
dev.off()
```

## CN/GE

```{r CN_GE, eval = FALSE, fig.height=10, fig.width=15}
# Copy number
